---
title: "Maxent Obis"
author: "Jace"
date: "7/14/2021"
output: html_document
---

```{r}
library(raster)
library(robis)
library(tidyverse)
library(lubridate)
library(dismo)
source('MURsst-points.R')
```


## SST background genoration

will load in the existing background points from the CSV 'SSTsample.csv' so that the next chunck can add to it

```{r}
taxon.name <- 'Karenia brevis'  #taxon of interest



read.csv("SSTsample.csv") %>% 
select(!X) %>% 
mutate(date= ymd(date))->rsst

```

This chunk will collect SST points from random long and lat from random days from the MUR database from 2002 to 2020

the output is a CSV with new points added
```{r}

# for (i in 1:9999) {
#   
#    
# lo<-(runif(1, min = -180, max = 180))
# la<-runif(1, min = -90, max = 90)
# la<-180*asin(la/90)/pi
# year<-round(runif(1, min = 2002.5, max = 2020.49))
# month<-round(runif(1, min = .5, max = 12.49))
# day<-round(runif(1, min = .5, max = 28.49))
# 
# points <-tribble(
#   ~lon, ~lat, ~date,
#   lo,  la,   (paste0(year,"-",month,"-",day)))
#  
# loop_tabl <- MURpoints(points)
# 
# rsst<- add_row(rsst,loop_tabl)
# }
# 
# 
# write.csv(rsst, "SSTsample.csv")

  
```

## OBIS get data

```{r}

taxon.data <- robis::occurrence(taxon.name)

```


## Maxent data prep


formats data to vectors that for input into Maxent function

```{r}
read.csv("SSTsample.csv") %>% 
select(!X) %>% 
mutate(date= ymd(date))->rsst


x<-rsst$analysed_sst[!is.na(rsst$analysed_sst)]-273.15

y<-taxon.data$sst[!is.na(taxon.data$sst)] #Data from the other RMD that loads in the OBIS data



#prepares the background and sampled data to input into the Maxent function
obs<-c(y,(x )) 
labs<-c(rep(1,length(y)),rep(0,length(x)))
```


Runs Maxent function
```{r}
maxent(as.data.frame(obs),as.data.frame(labs)) ->model

response(model)



```




